\tool

### 2018-05-10 paper/paper.tex
Updated images and added references to text

@@

Our approach uses three design pillars to increase awareness of software engineering tools: \textit{commend} developers on their work, \textit{apprehend} additional opportunities for improvement, and \textit{recommend} useful development tools to enhance the quality of the code.

@@

To determine improvements in code quality, our approach monitors problems reported by the output of software engineering tools. For example, suppose we want to use our approach to increase awareness of useful refactoring tools. To do this, our technique will inspect code changes made by developers to determine if a refactoring activity occurs. If a refactoring activity is detected, then we commend the programmer for their work to improve the quality of the code.

@@

After commending software engineers for their work, our approach automatically finds opportunities to make similar changes to improve the code. For example, after the programmer completes the refactoring task, we analyze the entire updated version of the code base to find other places where the same refactoring activity is applicable.

@@

The final step of our approach is to recommend useful software engineering tools to developers. The recommendation to developers includes commending them for improving code quality and apprehending new opportunities for similar improvements. In our example, the recommendation to the developer will praise them for their work refactoring the code, provide additional places in the code where they can make similar refactoring changes, and then suggest the refactoring tool which is useful for detecting even more instances for refactoring activities. Our goal is that through commending and apprehending, we can improve the effectiveness of recommendations for software engineering tools and increase adoption among developers. Figure \ref{fig:chartA} provides a general overview of how our approach can be implemented as an active help system.

%TODO: All non-lossy images
\begin{figure*}
	\includegraphics[width=\textwidth]{images/flowchartA.png}
	\caption{Flowchart presenting a general implementation of our approach}	
	\label{fig:chartA} 
\end{figure*}

@@

First, a GitHub user makes a change to a repository. \tool~automatically analyzes to commits and pull requests GitHub projects to find opportunities to commend developers when bugs reported by \textsc{Error Prone} are removed. \textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code. Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}. More details on how our implementation determines a bug fix can be found in Section 6.2.

@@

Next, \tool~apprehends places where similar opportunities to the code can be made. GitHub should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing. \tool~suggests \textsc{Error Prone} when a reported bug is fixed by a developer in a commit or pull request, but the same error still exists elsewhere in the code.

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{images/flowchartB.png}
	\caption{Flowchart presenting how we implemented our approach in \tool}	
	\label{fig:chartB} 
\end{figure*}

@@

To analyze 700+ GitHub repositories simultaneously, we set up \tool~on virtual machines. We used Ansible\footnote{https://www.ansible.com/} to automatically generate and provision Jenkins jobs for every project. To limit the load on each machine, we ran our study in parallel by dividing the Jenkins jobs among \textit{n} virtual CentOS images. The scripts and instructions to used setup our study environment for \tool~are publicly available to view online.

@@

We manually reviewed each instance where \tool~reported a recommendation to a developer for two reasons. First, we wanted to ensure that only one \textsc{Error Prone} recommendation was made to each project. This avoids biasing our results by minimizing the chance other GitHub users working on the same project discover the tool from a comment made to that repository. Additionally, in some cases one commit or pull request provided multiple opportunities for a recommendation. In this case, the authors examined each instance and selected one of errors reported  to make a recommendation on.

>>>>

\begin{figure*}
	\includegraphics[width=\textwidth]{images/flowchartA.png}
	\caption{Flowchart presenting a general implementation of our approach: \textit{A) Store project source code; B) Check for code changes; C.1) Add tool plugin, run tool on original code, and collect output; C.2) Add tool plugin, run tool on modified code, and collect output; D) Check for development tasks performed between versions of code; E) Search for other places where task can be applied; F) Recommend tool to help perform task.}}	
	\label{fig:chartA} 
\end{figure*}

@@

Our approach uses three design pillars to increase awareness of software engineering tools: \textit{commend} developers on their work, \textit{apprehend} additional opportunities for improvement, and \textit{recommend} useful development tools to enhance the quality of the code. Figure \ref{fig:chartA} provides a general overview of how we implement these design pillars as an active help system.

@@

To determine improvements in code quality, our approach monitors projects for code changes made by software engineers (Figure \ref{fig:chartA}A, \ref{fig:chartA}.B). Software engineering tools are used to determine if programming tasks are performed by developers when they make code changes by automatically runs tools on the original version of the code and the modified version (Figure \ref{fig:chartA}.C). Then, we compare the tool output from on both versions of code to determine if any development tasks were performed by the developer (Figure \ref{fig:chartA}.D). For example, if we want to recommend a refactoring tool to a developer in an Integrated Development Environment (IDE), then we would wait for changes to the code base and use a tool to detect if a refactoring activity occured in the modifications. If a refactoring activity is detected, our approach commends the programmer for their code change to improve the software quality when making a recommendation for the refactoring tool.

@@

After determining whether a development activity occured, our approach searches for similar instances in the code where the same activity can be applied. To apprehend opportunities for similar programming tasks, our approach involves automatically analyzing the tool output from the updated code to automatically find new opportunities where developers can perform the same task  (Figure \ref{fig:chartA}.E). For example, after the programmer completes the refactoring task in the IDE our approach analyzes the entire updated version of the code base to find other places where the same refactoring activity is applicable.

@@

The final step of our approach is to recommend software engineering tools to developers  (Figure \ref{fig:chartA}.F). The recommendation to developers includes commending them for improving code quality based on their changes and apprehending new opportunities to make the same improvement. In the continuing example, after determining refactoring activity was performed and finding other locations in the code where the same task can be performed, then our approach will make a recommendation to the developer in the IDE. The recommendation will praise the developer for their refactoring change, provide additional places in the code where they can make the same refactoring change, and suggest using a refactoring tool for future refactoring activities. Our goal is that through commending and apprehending, we can improve the effectiveness of recommendations for software engineering tools and increase adoption among developers.

@@

First, we clone repositories locally to detect when GitHub users make changes to a project as a commit or pull request (Figure \ref{fig:chartB}.A.3,  \ref{fig:chartB}.B). \tool~automatically analyzes code changes to find opportunities to commend developers when bugs reported by \textsc{Error Prone} are removed. \textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code. Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}. More details on how our implementation determines a bug fix can be found in Section 6.2.

@@

Next, \tool~apprehends places where similar opportunities to the code can be made (Figure \ref{fig:chartA}.E). GitHub developers should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing. \tool~suggests \textsc{Error Prone} when a reported bug is fixed by a developer in a commit or pull request, but the same error still exists elsewhere in the code.

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{images/flowchartB.png}
	\caption{Flowchart presenting our implementation of \tool~for this evaluation: \textit{A) Store project source code; B) Check for code changes; C.1) Add tool plugin, run tool on original code, and collect output; C.2) Add tool plugin, run tool on modified code, and collect output; D) Check for development tasks performed between versions of code; E) Search for other places where task can be applied; F) Recommend tool to help perform task.}}	
	\label{fig:chartB} 
\end{figure*}

@@

To analyze 700+ GitHub repositories simultaneously, we set up \tool~on virtual machines. We used Ansible\footnote{https://www.ansible.com/} to automatically setup and install dependencies on the all the virtual machines, and then on each VM we use it to setup the Jenkins server and generate Jenkins jobs for each project. Each Jenkins job clones the GitHub repository, periodically checks for new commits and pull requests every 15 minutes, and runs \tool~to analyze project code changes. Figure \ref{fig:chartB}.A.1-A.3 displays the setup process for our evaluation of \tool. Additionally, the scripts and instructions to setup the study environment are publicly available online.\footnote{\url{https://github.com/chbrown13/tool-recommender-bot/tree/master/eval_scripts/}}

@@

For our evaluation, we manually reviewed each instance where \tool~reported a recommendation to a developer. This step can be seen in Figure \ref{fig:chartB}.F. We do this for several reasons: First, we wanted to ensure that only one \textsc{Error Prone} recommendation was made to each project to avoid biasing our results by minimizing the chance other GitHub users working on the same project discover the tool from a comment made to that repository. Additionally, in some cases one commit or pull request provided multiple opportunities for a recommendation. In this case, the authors examined each instance and selected one of errors reported  to make a recommendation on.
